---
title: 'Lab 4: Exploring the Poisson Probability Distribution'
subtitle: "75694189 16257626 13341225"
author: "Chen Wang, Junke Wang, Zhuozhi Xiong"
date: "due: Oct 23, 2019 5:00 pm"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(tidyverse)
```

## Poisson Distributions

Functions: `dpois()`, `ppois()`, `qpois()`, `rpois()`

You run a computer server that services a local message board. Records indicate that messages arrive to the server at a rate of 6 per hour.

For each question below, write the code, then the text answer.

1. What is the expected value of this distribution? What is the variance?


In this question, lambda = 6/hour. And the expected value will be E(x) = lambda = 6 per hour.

Var(X) = lambda = 6 per hour^2. 

2. What is the probability that, in the next hour, the server will receive exactly 5 messages?

```{r}
dpois(x=5,6)
```

P(X=5) = 0.16


\newpage

3. What is the probability that the server will receive no more than 10 messages but at least 5 messages in the next 2 hours?

For two hours, the new lambda will be 6 * 2 = 12/two hours.

```{r}
dpois(5,12)+dpois(6,12)+dpois(7,12)+dpois(8,12)+dpois(9,12)+dpois(10,12)
```

P(5<=X<=10) = 0.34

4. What is the probability that, in the next 3 hours, the server will receive exactly 10 messages?

For the next 3 hours, the new lambda will be 6 * 3 = 18/three hours.

```{r}
dpois(10,18)
```

P(X=10) = 0.01

5. One of your friends says that there is only a 13% chance that the server will receive more than 8 messages in an hour. Are the correct? Why?

```{r}
1-ppois(8,6)
```

This is not true. Because P(X>8) = 0.15
